---
title: "Efficacy Titer Modeling"
author: "Olivia Rippee"
date: "`r Sys.Date()`"
output: word_document
---

## Kentucky: Modeling

```{r HAI titer Kentucky modeling}

# Logistic Regression (GLM)
# --------------------------
model_glm <- glm(Kentucky_Pos ~ Group * Day,
                 data = data_2026_KY_titer_incidence_5day,
                 family = binomial)

summary(model_glm)
anova(model_glm, test = "Chisq")
```

\pagebreak

## Kentucky: Estimated Marginal Means

```{r HAI titer Kentucky emm, eval=FALSE}

#  Estimated Marginal Means (Predicted Probabilities)
# ----------------------------------------------------
emm_all <- emmeans(model_glm,
                   ~ Group | Day,
                   type = "response")

print(emm_all)
```

\pagebreak

## Kentucky: Identify the Day Control Horses Seroconverted

```{r HAI titer Kentucky seroconversion}

emm_control <- emmeans(model_glm,
                       ~ Day | Group,
                       at = list(Group = "Control"),
                       type = "response")

control_comparisons <- pairs(emm_control, adjust = "tukey")

print(emm_control)
print(control_comparisons)

```

\pagebreak

## Kentucky: Demonstrate IVP Remained Seronegative

```{r HAI titer Kentucky IVP seronegative}

emm_ivp <- emmeans(model_glm,
                   ~ Day | Group,
                   at = list(Group = "IVP"),
                   type = "response")

ivp_comparisons <- pairs(emm_ivp, adjust = "tukey")

print(emm_ivp)
print(ivp_comparisons)
```

\pagebreak

## Kentucky: Demonstrate Both Groups Were Seronegative at Day 0

```{r HAI titer Kentucky seronegative day 0}

emm_day0 <- emmeans(model_glm,
                    ~ Group | Day,
                    at = list(Day = "0"),
                    type = "response")

baseline_comparison <- pairs(emm_day0)

print(emm_day0)
print(baseline_comparison)

```

\pagebreak

## Richmond: Modeling

```{r HAI titer Richmond modeling}

# Logistic Regression (GLM)
# --------------------------
model_glm <- glm(Richmond_Pos ~ Group * Day,
                 data = data_2026_RM_titer_incidence_5day,
                 family = binomial)

summary(model_glm)
anova(model_glm, test = "Chisq")

```

\pagebreak

## Richmond: Estimated Marginal Means

```{r HAI titer Richmond emm}

#  Estimated Marginal Means (Predicted Probabilities)
# ----------------------------------------------------
emm_all <- emmeans(model_glm,
                   ~ Group | Day,
                   type = "response")

print(emm_all)

```

\pagebreak

## Richmond: Identify the Day Control Horses Seroconverted

```{r HAI titer Richmond control seroconversion}

emm_control <- emmeans(model_glm,
                       ~ Day | Group,
                       at = list(Group = "Control"),
                       type = "response")

control_comparisons <- pairs(emm_control, adjust = "tukey")

print(emm_control)
print(control_comparisons)
```

\pagebreak

## Richmond: Demonstrate IVP Remained Seronegative

```{r HAI titer Richmond IVP seronegative}

emm_ivp <- emmeans(model_glm,
                   ~ Day | Group,
                   at = list(Group = "IVP"),
                   type = "response")

ivp_comparisons <- pairs(emm_ivp, adjust = "tukey")

print(emm_ivp)
print(ivp_comparisons)
```

\pagebreak

## Richmond: Demonstrate Both Groups Were Seronegative at Day 0

```{r HAI titer Richmond seronegative day 0}

emm_day0 <- emmeans(model_glm,
                    ~ Group | Day,
                    at = list(Day = "0"),
                    type = "response")

baseline_comparison <- pairs(emm_day0)

print(emm_day0)
print(baseline_comparison)

```
 